Modelling the gas kinematics of an atypical Lyman-alpha emitting compact dwarf galaxy

### 2017-09-15 paper/paper.tex
minor edtis

The preferred value for the rotational velocity can be explained as
follows. 
Lower rotational velocities than the favored value would produce a
double peaked line as the different doppler shifts produced on
different regions of the rotating sphere would not be large enough to
smear the double peaks into a single peak
\citep{GaravitoCamargo2014}. 
For the same reason, higher rotation velocities could produce a single
peak but the line would be broader than it is observed.
The fact that the velocity and optical depth priors were wide enough,
allows us to suggest that the current values for the spherical model
found by the MCMC are robust given the observational constraints.

@@

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial sampling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and prominent emission lines to finally compute velocity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }

@@

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This should be considered an an upper bound as lower values
  could be achieved if one considers instead a cored DM profile.}
{\bf Realistic mass estimates could only be achieved by detailed mass
  modelling once \tol's detailed kinematic information becomes
  available.}

@@

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved the paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.
We are thankful to the community developing and maintining open source
packages fundamental to our work: numpy \& scipy \citep{numpy}, the
Jupyter notebook \citep{IPython,jupyter}, matplotlib
\citep{matplotlib}, astropy \citep{astropy},  scikit-learn
\citep{scikit-learn}, pandas \citep{pandas} and daft
(\url{http://daft-pgm.org/}).

>>>>

The preferred value for the rotational velocity can be explained as
follows. 
Lower rotational velocities than the favored value would produce a
double peaked line as the different doppler shifts produced on
different regions of the rotating sphere would not be large enough to
smear the double peaks into a single peak
\citep{GaravitoCamargo2014}. 
For the same reason, higher rotation velocities could produce a single
/eak but the line would be broader than it is observed.
The fact that the velocity and optical depth priors were wide enough,
allows us to suggest that the current values for the spherical model
found by the MCMC are robust given the observational constraints.

@@

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial sampling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine Blue Compact Galaxies (BCGs) to produce two-dimensional maps of the
continuum and prominent emission lines to finally compute velocity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }

@@

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This should be considered an upper bound as lower values
  could be achieved if one considers instead a cored DM profile.}
{\bf Realistic mass estimates could only be achieved by detailed mass
  modelling once \tol's detailed kinematic information becomes
  available.}

@@

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved the paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.
We are thankful to the community developing and maintaining open source
packages fundamental to our work: numpy \& scipy \citep{numpy}, the
Jupyter notebook \citep{IPython,jupyter}, matplotlib
\citep{matplotlib}, astropy \citep{astropy},  scikit-learn
\citep{scikit-learn}, pandas \citep{pandas} and daft
(\url{http://daft-pgm.org/}).
